\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
\begin{otherlanguage}{british}
	This document shows the development of an Internet voting solution to be used to hold the Elections for the Junta de Escuela in the Escuela Politécnica Superior of the Universidad San Pablo CEU, placed in Madrid, Spain. \\
	
	It tries to offer a proof of concept of a secure Internet voting system which uses the new \gls{DNIe} 3.0 as a tool for the remote voter identification. \\
	
	At the moment of writing this document, there are several solutions implemented to solve this kind of problems, but there is none system which allow the use of the new Spanish ID card to identify the voter remotely. \\
	
	The goal of this project, along with the implementation of the solution, is that it will serve as a start point for future developments with voting and  the new \gls{DNIe} with \gls{NFC} chip. \\
	
	So then, we can consider that this project establishes the first Internet voting system that uses the \gls{DNIe} 3.0 to identify the voter using its \gls{NFC} chip. \\
	
	To accomplish the solution, it has been decided to adapt an existing solution, Helios Voting. This project, created by Ben Adida in the \gls{MIT}, is considered as a de-facto standard in electronic voting based in End-to-end Verifiability protocols and a homomorphic cryptography. It is the more complete free software project for low coercion risk elections. \\
	
	Neverthless, to fulfill the goals of this \gls{PFC}, which includes the use of the\gls{DNIe} as digital user identification, it has been necessary a system integration. Helios Voting, though it offers several login options, it does not support digital certificates login by default, which is basic for using the ones included in the \gls{DNIe} card. This causes the need to design an alternative identification module, based in oAuth 2.0 protocol with a web server configured to accept these digital certificates. \\
	
	To ease the use of this document, an Android app developed by Spanish Police Department has been integrated. This app has needed to be adapted in order to fulfill the requirements of the project, but it allows the voters to use their mobile devices to cast a vote using their \gls{NFC} sensor and their own \gls{DNIe} 3.0 cards, with no needs of external hardware as contact chip readers. This approach makes possible to cast votes from anywhere with an Internet connection. \\
\end{otherlanguage}